Persistence of seed mixture species: <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-15 R/model_persistence_markdown.Rmd
Update

```{r}
iter = 10000
chains = 4
thin = 2
priors <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("normal(-0.025, 1)", class = "b", coef = "sand_ratio25"),
  set_prior("normal(-0.050, 1)", class = "b", coef = "sand_ratio50"),
  set_prior("normal(0.050, 1)", class = "b", coef = "expositionsouth"),
  set_prior("normal(-0.025, 1)", class = "b", coef = "survey_year_fct2019"),
  set_prior("normal(-0.050, 1)", class = "b", coef = "survey_year_fct2020"),
  set_prior("normal(-0.075, 1)", class = "b", coef = "survey_year_fct2021"),
  set_prior("cauchy(0, 1)", class = "sigma")
)
```

>>>>

```{r}
iter = 10000
chains = 4
thin = 2
priors <- c(
  set_prior("normal(0, 20)", class = "b"),
  set_prior("normal(-2.5, 20)", class = "b", coef = "sand_ratio25"),
  set_prior("normal(-5, 20)", class = "b", coef = "sand_ratio50"),
  set_prior("normal(5, 20)", class = "b", coef = "expositionsouth"),
  set_prior("normal(-2.5, 20)", class = "b", coef = "survey_year_fct2019"),
  set_prior("normal(-5, 20)", class = "b", coef = "survey_year_fct2020"),
  set_prior("normal(-7.5, 20)", class = "b", coef = "survey_year_fct2021"),
  set_prior("cauchy(0, 10)", class = "sigma")
)
```
